new_analses

### 2021-07-14 new_analyses.Rmd
k
jh

```{r}
library(patchwork)
f1 <- p1c | p1f | p1s +
  plot_annotation(
  title = "DOY of 10, 50, and 90% Palmer amaranth flowering after first transplanting") 
  ggsave("June.png", width = 9, height = 5, dpi = 600, f1)
```

@@

```{r}
library(patchwork)
f3 <- p2c | p2f | p2s +
  plot_annotation(
  title = "DOY of 10, 50, and 90% Palmer amaranth flowering after second transplanting") 
  ggsave("July.png", width = 9, height = 5, dpi = 600, f3)
```

@@

```{r}
f4 <- fg1 | fg2 | fg3 +
  plot_annotation(
  title = NULL) 
  ggsave("biomass.png", width = 9, height = 5, dpi = 600, f4)
```

@@

```{r}
f5 <- fg4 | fg5 | fg6 +
  plot_annotation(
  title = NULL) 
  ggsave("height.png", width = 9, height = 5, dpi = 300, f5)
```

@@

```{r}
library(patchwork)
f3 <- p1c | p2c +
  plot_annotation(
  title = "DOY of 10, 50, and 90% Palmer amaranth flowering") 
  ggsave("Combined.png", width = 6, height = 5, dpi = 600, f3)
```

@@

ggsave("first.png", width = 3)
```

@@

ggsave("second.png", width = 3)
```

@@

ggsave("biomass.png", width = 6)
```

@@

```{r}
data1 %>% 
  filter(!is.na(weight)) %>% 
  group_by(location, month, crop, doyh) %>% 
  summarise(biomass = sum(weight))  %>% 
  ggplot(aes(x = biomass, y = crop)) +
  geom_density_ridges() +
  facet_grid(location ~ month)
```

@@

ggsave("biomass.png")
```

>>>>

```{r}
library(patchwork)
f1 <- p1c | p1f | p1s +
  plot_annotation(
  title = "DOY of 10, 50, and 90% Palmer amaranth flowering after first transplanting") 
  ggsave("figures/June.png", width = 9, height = 5, dpi = 600, f1)
```

@@

```{r}
library(patchwork)
f3 <- p2c | p2f | p2s +
  plot_annotation(
  title = "DOY of 10, 50, and 90% Palmer amaranth flowering after second transplanting") 
  ggsave("figures/July.png", width = 9, height = 5, dpi = 600, f3)
```

@@

```{r}
f4 <- fg1 | fg2 | fg3 +
  plot_annotation(
  title = NULL) 
  ggsave("figures/biomass.png", width = 9, height = 5, dpi = 600, f4)
```

@@

```{r}
f5 <- fg4 | fg5 | fg6 +
  plot_annotation(
  title = NULL) 
  ggsave("figures/height.png", width = 9, height = 5, dpi = 300, f5)
```

@@

```{r}
library(patchwork)
f3 <- p1c | p2c +
  plot_annotation(
  title = "DOY of 10, 50, and 90% Palmer amaranth flowering") 
  ggsave("figures/Combined.png", width = 6, height = 5, dpi = 600, f3)
```

@@

ggsave("figures/first.png", width = 3)
```

@@

ggsave("figures/second.png", width = 3)
```

@@

ggsave("figures/biomass.png", width = 6)
```

```{r}
biom %>%
  group_by(month) %>% 
  nest(-month) %>% 
  mutate(model = map(data, ~ lmer(log(biomass) ~ crop + 
                                 (1|year/location), data = .x)),
         anova = map(model, anova),
         emmeans = map(model, ~ emmeans(., ~ crop, 
                                        type = "response"))) -> analysis2
```

```{r}
#anova
analysis2$anova[[2]]
```

```{r}
analysis2$emmeans[[2]] %>% 
  as_tibble() %>% 
  mutate(month = "Second transplanting") -> second2

analysis2$emmeans[[1]] %>% 
  as_tibble() %>% 
  mutate(month = "First transplanting") %>% 
  bind_rows(second2) -> result2
```

```{r}
result2 %>% 
  filter(month == "First transplanting") %>% 
  ggplot(aes(x = crop, y = response,
             color = crop)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL)) +
  scale_color_manual(values = c(1,2,4,3,5, 1,3,2,4,5, 1,2,4,3,5)) +
  facet_grid(~ month, scales = "free") +
  coord_flip() +
  ylim(0, 30) +
  labs(y = expression(paste("Biomass (g plant "^"-1",")")), x = NULL) +
  theme_test() +
  theme(legend.position = "none") -> first

ggsave("figures/first_crop.png", width = 3)
```

```{r}
theme_set(theme_test(base_family = "roboto"))
result2 %>% 
  filter(month == "Second transplanting") %>% 
  ggplot(aes(x = crop, y = response,
             color = crop)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL)) +
  scale_color_manual(values = c(1,2,3,4,5, 1,4,2,3,5, 1,2,3,4,5)) +
  facet_grid(crop ~ month, scales = "free") +
  coord_flip() +
  labs(y = expression(paste("Biomass (g plant "^"-1",")")), x = NULL) +
  theme_test() +
  theme(legend.position = "none") -> second

ggsave("figures/second_crop.png", width = 3)
```

ggsave("figures/biomass.png", width = 6)
```

@@

@@

ggsave("figures/biomass.png")
```
